---
title: "lab02-sam-na-pt2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Sorry for two parts, I kept getting a pandoc error when it was all on one rmd
```{r}
library(dplyr)
data(starwars)
starwars <- na.omit(starwars[ ,c(1,2,3,8,9)])
#Init
name <- starwars$name
height <- starwars$height
mass <- starwars$mass
gender <- starwars$gender
homeworld <- starwars$homeworld
four <- head(name, n = 4)
```
##Matrix Practice

# Females
```{r}
#MH
MH <- cbind(mass[1:10], height[1:10])
#FEMALES
females <- matrix(c(mass[gender == "female"], height[gender == "female"]), nrow = length(mass[gender == "female"]), ncol = 2)
#Females Row and Col Names
rownames(females) <- name[gender == 'female']
colnames(females) <- c("Height", "Mass")
females
```

#Males
```{r}
#MALES
males <- matrix(c(mass[gender == "male"], height[gender == "male"]), nrow = length(mass[gender == "male"]), ncol = 2)
#Males Row and Col Names
rownames(males) <- name[gender == 'male']
colnames(males) <- c("Height", "Mass")
males
```

```{r}
#FM
FM <- rbind(females[1:5,], males[1:5,])
FM
```


```{r}
#Reversed FM
revFM <- apply(FM, 2, rev)
revFM
```

```{r}
#Last Row of FM
lastFM <- FM[10,]
lastFM
```

```{r}
#Reversed FM Cols
FM[, c(1, 2)] <-  FM[, c(2, 1)]
colnames(FM)[c(1, 2)] <-  colnames(FM)[c(2, 1)]
FM
```

```{r}
#MHW Data Type
MHW <- matrix(c(mass, height, gender), nrow = length(mass), ncol = 3)
typeof(MHW)
```

## Dataframe Practice
```{r}
#Select First Row
head(starwars, 1)

#First 5 Columns Name and Homeworld
namehomeworld <-  starwars
namehomeworld %>% select("name", "homeworld")
head(namehomeworld, 5)

#Han Solo's Info
subset(starwars, name == "Han Solo")

#Smallest Height
subset(starwars, height == height[which.min(height)])

#Females
subset(starwars, gender == 'female')

#Females Less Mass 50
subset(starwars, gender == 'female' & mass < 50)

#Name and Gender of Height Less than 160
hgtless <-  subset(starwars, height<160)
hgtless %>% select("gender", "homeworld")

#Alphabetical Order
ordered <- starwars[order(name),]
head(ordered, 8)

#New Column heightmass
starwars$heightmass = height * mass
starwars

