---
title: "lab04-sam-na"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "images/")
```

```{r}
library(dplyr)
```

# Abalone Data Set

Character delimiter is commas, there isn't a row for column names, there are no missing attribute values, and the data types of each column is nominal for the "sex" column, continuous for the "length, diameter, height, whole weight, shucked weight, viscera weight, and shell weight" columns, and integer for the "rings" column.

---

# Bash Commands

```{r eval = FALSE}
file abalone.data
wc abalone.data
wc -l abalone.data
head abalone.data
head -n5 abalone.data
tail abalone.data
tail -n3 abalone.data
less abalone.data
```

---

# Basic Importing

```{r}
column_names <- c("Sex", "Length", "Diameter", "Height", "Whole Weight", "Shucked Weight", "Viscera Weight", "Shell Weight", "Rings")
column_types <- c("character", "real", "real", "real", "real", "real", 'real', 'real', 'integer')
abalone <- read.table("abalone.data", sep = ",", col.names = column_names, colClasses=column_types)
head(abalone)
str(abalone)

###
abalone2 <- read.csv("abalone.data")
head(abalone2)
str(abalone2)

###
abalone10 <- read.table("abalone.data", sep = ",", nrows=10)
abalone10
str(abalone10)

###
abalone20 <- read.table("abalone.data", sep = ",", skip=10)
head(abalone20)
str(abalone20)

###
minabalone <- apply(abalone[-1], 2, min)
maxabalone <- apply(abalone[-1], 2, max)
meanabalone <- apply(abalone[-1], 2, mean)
sdabalone <- apply(abalone[-1], 2, sd)
rbind(minabalone, maxabalone, meanabalone, sdabalone)
```

---

# Intro to GGPLOT2
```{r}
library(ggplot2)
coltype <- c("character", "factor", "factor", "integer", "integer", "integer", "integer", "character", "real", "real", "real", "real", "real", "real", "real")
nba <- read.csv("data/nba2018-players.csv", sep=",", colClasses = coltype)
str(nba)
```

```{r HeightWeightScatter}
ggplot(data = nba, aes(x = height, y = weight)) + geom_point()
```

```{r HWText}
ggplot(data = nba, aes(x = height, y = weight)) + geom_text(aes(label=player))
```

```{r HWLabel}
ggplot(data = nba, aes(x = height, y = weight)) + geom_label(aes(label=player))
#Difference is label surrounds the text with a white box for slightly better readability and less text overlap.
```

```{r SalaryDensity}
ggplot(nba, aes(salary)) + geom_density()
```

```{r Points2Hist}
ggplot(nba, aes(points2)) + geom_histogram(binwidth=50)
```

```{r PositionBar}
ggplot(nba, aes(position)) + geom_bar()
```

```{r ExpSalScatter}
ggplot(filter(nba, position == "C"), aes(experience, salary)) + geom_point() + geom_smooth(method = "lm")
```

```{r ExpSalScatterLoess}
ggplot(filter(nba, position == "C"), aes(experience, salary)) + geom_point() + geom_smooth(method = "loess")
```

---

# Faceting

```{r ExpSalScatterFacet}
ggplot(nba, aes(experience, salary)) + geom_point() + facet_wrap(~ position)
```

```{r ExpSalScatterFacetTeam}
ggplot(nba, aes(experience, salary)) + geom_point() + facet_wrap(~ team)
```

```{r AgeTeamFacet}
ggplot(nba, aes(age)) +geom_density() + facet_wrap(~ team)
```

```{r HWPositionFacet}
ggplot(nba, aes(height, weight)) + geom_point() + facet_wrap(~ position)
```

```{r HW2dPositionFacet}
ggplot(nba, aes(height, weight)) + geom_density2d() + facet_wrap(~ position)
```

```{r ExpSalWarriors}
ggplot(filter(nba, team == "GSW"), aes(experience, salary)) + geom_point() + theme_bw()
```

```{r LayerFun}
ggplot(nba, aes(height, weight)) + geom_density2d() + facet_wrap(~ position) + theme_minimal()
```

---

# Shell Commandos

```{r eval=FALSE}
cd images
ls
ls -l
ls -l -t
ls -r
mkdir ../copies
cp SalaryDensity-1.png ../copies
cp *png ../copies
cd ../copies
mv SalaryDensity-1.png SD.png
cd ../report
mv ../copies ../copy-files
rm ../copy-files/SD.png
rmdir -r ../copy-files
```